Reproducibility in Plant Pathology

### 2018-04-08 README.rmd
Clean up README

This repository is organized as an R package. There is one R function,
`doi2bib()`, that is used in this repository, along with the data,
`assigned_article_notes.rda` that are located in `data` directory. We have used
the R package structure to help manage dependencies, to take advantage of
continuous integration for automated code testing and for file organisation.

@@

We developed and tested the package on this Docker container, so this is the only platform that we're confident it works on, and so recommend to anyone wanting to use this package to generate the vignette, etc.

>>>>

This repository is organized as an R package. There is one R function,
`doi2bib()`, that is used in this repository, along with a bibliography file of
the articles that were examined that are located in `inst/extdata` directory. We
have used the R package structure to help manage dependencies, to take advantage
of continuous integration for automated code testing and for file organisation.

@@

We developed and tested the package on this Docker container, so this is the
only platform that we're confident it works on, and so recommend to anyone
wanting to use this package to generate the vignettes, etc.
